---
title: "CPSC 540 - Homework 1: Marketing Campaign Analysis"
author: "Matthew Tonks"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  tidy = TRUE,
  size = "vsmall",
  cache = TRUE,
  fig.align = 'center',
  fig.width = 10,
  fig.height = 6
)

# Set seed for reproducibility
set.seed(1818)

# Load required libraries
library(tidyverse)
library(broom)
library(MASS)
library(mgcv)
library(performance)
library(see)
library(gridExtra)
library(knitr)
library(car)

# Set options
options(width = 70)
options(scipen = 99)
```

# Data Loading and Preparation

```{r load-data}
# Load the marketing campaign data
data <- read_csv("marketingcampaign.csv")

# Display structure
glimpse(data)

# Summary statistics
summary(data)

# Check for missing values
sum(is.na(data))
```

```{r data-preparation}
# Convert categorical variables to factors
data <- data %>%
  mutate(
    gender = factor(gender),
    campaign_variant = factor(campaign_variant, levels = c("A", "B", "C")),
    ad_source = factor(ad_source),
    email_signup = factor(email_signup)
  )

# Verify conversion
str(data)
```

# Exploratory Data Analysis

## Overall Data Distribution

```{r eda-distributions}
# Create distribution plots for numeric variables
p1 <- ggplot(data, aes(x = age)) +
  geom_histogram(bins = 30, fill = "steelblue", alpha = 0.7) +
  labs(title = "Age Distribution", x = "Age", y = "Count") +
  theme_minimal()

p2 <- ggplot(data, aes(x = past_purchases)) +
  geom_histogram(bins = 30, fill = "darkgreen", alpha = 0.7) +
  labs(title = "Past Purchases Distribution", x = "Past Purchases", y = "Count") +
  theme_minimal()

p3 <- ggplot(data, aes(x = campaign_spend)) +
  geom_histogram(bins = 30, fill = "coral", alpha = 0.7) +
  labs(title = "Campaign Spend Distribution", x = "Campaign Spend ($)", y = "Count") +
  theme_minimal()

grid.arrange(p1, p2, p3, ncol = 2)
```

```{r eda-categorical}
# Categorical variable distributions
p4 <- ggplot(data, aes(x = gender)) +
  geom_bar(fill = "purple", alpha = 0.7) +
  labs(title = "Gender Distribution", x = "Gender", y = "Count") +
  theme_minimal()

p5 <- ggplot(data, aes(x = campaign_variant)) +
  geom_bar(fill = "orange", alpha = 0.7) +
  labs(title = "Campaign Variant Distribution", x = "Campaign Variant", y = "Count") +
  theme_minimal()

p6 <- ggplot(data, aes(x = ad_source)) +
  geom_bar(fill = "darkblue", alpha = 0.7) +
  labs(title = "Ad Source Distribution", x = "Ad Source", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p7 <- ggplot(data, aes(x = email_signup)) +
  geom_bar(fill = "darkred", alpha = 0.7) +
  labs(title = "Email Signup Distribution", x = "Email Signup", y = "Count") +
  theme_minimal()

grid.arrange(p4, p5, p6, p7, ncol = 2)
```

---

# Question 1: What kinds of people make MORE purchases?

## Question 1 Exploratory Analysis

```{r q1-exploration}
# Relationship between age and past purchases
ggplot(data, aes(x = age, y = past_purchases)) +
  geom_point(alpha = 0.3, color = "steelblue") +
  geom_smooth(method = "loess", color = "darkred", se = TRUE) +
  labs(
    title = "Relationship between Age and Past Purchases",
    x = "Age",
    y = "Past Purchases"
  ) +
  theme_minimal()
```

```{r q1-by-gender}
# Past purchases by gender
ggplot(data, aes(x = gender, y = past_purchases, fill = gender)) +
  geom_boxplot(alpha = 0.7) +
  labs(
    title = "Past Purchases by Gender",
    x = "Gender",
    y = "Past Purchases"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

# Summary statistics by gender
data %>%
  group_by(gender) %>%
  summarise(
    mean_purchases = mean(past_purchases),
    median_purchases = median(past_purchases),
    sd_purchases = sd(past_purchases),
    n = n()
  ) %>%
  kable(digits = 2, caption = "Past Purchases Summary by Gender")
```

```{r q1-by-email}
# Past purchases by email signup status
ggplot(data, aes(x = email_signup, y = past_purchases, fill = email_signup)) +
  geom_boxplot(alpha = 0.7) +
  labs(
    title = "Past Purchases by Email Signup Status",
    x = "Email Signup",
    y = "Past Purchases"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

# Summary statistics by email signup
data %>%
  group_by(email_signup) %>%
  summarise(
    mean_purchases = mean(past_purchases),
    median_purchases = median(past_purchases),
    sd_purchases = sd(past_purchases),
    n = n()
  ) %>%
  kable(digits = 2, caption = "Past Purchases Summary by Email Signup")
```

```{r q1-correlation}
# Correlation between numeric variables
cor_matrix <- data %>%
  select(age, past_purchases, campaign_spend) %>%
  cor()

cor_matrix %>%
  kable(digits = 3, caption = "Correlation Matrix")
```

## Question 1 Model Selection

Since `past_purchases` is a count variable (discrete, non-negative integers), we should consider:

1. **Poisson Regression**: For count data with equal mean and variance
2. **Negative Binomial Regression**: For count data with overdispersion (variance > mean)
3. **Linear Regression**: As a baseline comparison (though not ideal for count data)

```{r q1-check-overdispersion}
# Check if data is overdispersed
mean_purchases <- mean(data$past_purchases)
var_purchases <- var(data$past_purchases)

cat("Mean of past_purchases:", mean_purchases, "\n")
cat("Variance of past_purchases:", var_purchases, "\n")
cat("Variance/Mean ratio:", var_purchases / mean_purchases, "\n")

# If ratio >> 1, we have overdispersion and should use Negative Binomial
```

The variance/mean ratio indicates **overdispersion**, so Negative Binomial Regression is more appropriate than Poisson.

## Question 1 Models

### Model 1: Negative Binomial Regression (Full Model)

```{r q1-model-nb-full}
# Fit negative binomial regression with all predictors
model_q1_nb <- glm.nb(
  past_purchases ~ age + gender + email_signup + ad_source + campaign_variant + campaign_spend,
  data = data
)

# Summary
summary(model_q1_nb)

# Tidy output
tidy(model_q1_nb, conf.int = TRUE) %>%
  kable(digits = 3, caption = "Negative Binomial Model: Coefficient Estimates")
```

### Model 2: Simplified Negative Binomial Model

```{r q1-model-nb-simple}
# Based on initial results, fit a simplified model with significant predictors
model_q1_nb_simple <- glm.nb(
  past_purchases ~ age + email_signup + campaign_spend,
  data = data
)

# Summary
summary(model_q1_nb_simple)

# Compare models
AIC(model_q1_nb, model_q1_nb_simple)
BIC(model_q1_nb, model_q1_nb_simple)
```

### Model 3: Poisson Regression (for comparison)

```{r q1-model-poisson}
# Fit Poisson regression for comparison
model_q1_poisson <- glm(
  past_purchases ~ age + email_signup + campaign_spend,
  family = poisson(link = "log"),
  data = data
)

# Summary
summary(model_q1_poisson)

# Check for overdispersion in Poisson model
check_overdispersion(model_q1_poisson)
```

### Model 4: GAM with Smoothing for Age

```{r q1-model-gam}
# Fit GAM to allow non-linear relationship with age
model_q1_gam <- gam(
  past_purchases ~ s(age) + email_signup + s(campaign_spend),
  family = nb(),
  data = data
)

# Summary
summary(model_q1_gam)

# Plot smooth terms
plot(model_q1_gam, pages = 1, scheme = 2, main = "Smooth Terms in GAM Model")
```

## Question 1 Model Diagnostics

```{r q1-diagnostics}
# Residual plots for negative binomial model
par(mfrow = c(2, 2))
plot(model_q1_nb)
par(mfrow = c(1, 1))

# Check model assumptions
check_model(model_q1_nb)
```

```{r q1-predictions}
# Predicted vs actual
data_q1_pred <- data %>%
  mutate(
    predicted_nb = predict(model_q1_nb, type = "response"),
    predicted_gam = predict(model_q1_gam, type = "response")
  )

# Plot predictions
ggplot(data_q1_pred, aes(x = predicted_nb, y = past_purchases)) +
  geom_point(alpha = 0.3, color = "steelblue") +
  geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") +
  labs(
    title = "Predicted vs Actual Past Purchases (Negative Binomial)",
    x = "Predicted Purchases",
    y = "Actual Purchases"
  ) +
  theme_minimal()
```

## Question 1 Effect Interpretation

```{r q1-effects}
# Exponentiate coefficients for interpretation (incident rate ratios)
coef_exp <- exp(coef(model_q1_nb))
coef_ci_exp <- exp(confint(model_q1_nb))

results_q1 <- data.frame(
  Variable = names(coef_exp),
  IRR = coef_exp,
  Lower_CI = coef_ci_exp[, 1],
  Upper_CI = coef_ci_exp[, 2]
)

results_q1 %>%
  kable(digits = 3, caption = "Incident Rate Ratios (IRR) for Past Purchases")

# Visualize coefficients
tidy(model_q1_nb, conf.int = TRUE) %>%
  filter(term != "(Intercept)") %>%
  ggplot(aes(x = reorder(term, estimate), y = estimate)) +
  geom_point(size = 3, color = "steelblue") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  coord_flip() +
  labs(
    title = "Coefficient Estimates for Past Purchases Model",
    x = "Predictor",
    y = "Coefficient Estimate"
  ) +
  theme_minimal()
```

## Question 1 Key Findings

```{r q1-profile-analysis}
# Create profiles of high vs low purchasers
data_q1_profiles <- data %>%
  mutate(purchaser_type = ifelse(past_purchases > median(past_purchases), "High", "Low")) %>%
  group_by(purchaser_type) %>%
  summarise(
    avg_age = mean(age),
    pct_email_signup = mean(email_signup == "TRUE") * 100,
    avg_campaign_spend = mean(campaign_spend),
    n = n()
  )

data_q1_profiles %>%
  kable(digits = 2, caption = "Profile Comparison: High vs Low Purchasers")
```

---

# Question 2: Which campaign variant should Company X use?

## Question 2 Exploratory Analysis

```{r q2-exploration}
# Campaign spend by variant
ggplot(data, aes(x = campaign_variant, y = campaign_spend, fill = campaign_variant)) +
  geom_boxplot(alpha = 0.7) +
  labs(
    title = "Campaign Spend by Variant",
    x = "Campaign Variant",
    y = "Campaign Spend ($)"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

# Summary statistics by campaign variant
data %>%
  group_by(campaign_variant) %>%
  summarise(
    mean_spend = mean(campaign_spend),
    median_spend = median(campaign_spend),
    sd_spend = sd(campaign_spend),
    n = n()
  ) %>%
  kable(digits = 2, caption = "Campaign Spend Summary by Variant")
```

```{r q2-variant-by-demographics}
# Campaign spend by variant and gender
ggplot(data, aes(x = campaign_variant, y = campaign_spend, fill = gender)) +
  geom_boxplot(alpha = 0.7) +
  labs(
    title = "Campaign Spend by Variant and Gender",
    x = "Campaign Variant",
    y = "Campaign Spend ($)"
  ) +
  theme_minimal()

# Campaign spend by variant and email signup
ggplot(data, aes(x = campaign_variant, y = campaign_spend, fill = email_signup)) +
  geom_boxplot(alpha = 0.7) +
  labs(
    title = "Campaign Spend by Variant and Email Signup",
    x = "Campaign Variant",
    y = "Campaign Spend ($)"
  ) +
  theme_minimal()
```

```{r q2-spend-distribution}
# Distribution of campaign spend by variant
ggplot(data, aes(x = campaign_spend, fill = campaign_variant)) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Campaign Spend Distribution by Variant",
    x = "Campaign Spend ($)",
    y = "Density"
  ) +
  theme_minimal()

# Faceted histograms
ggplot(data, aes(x = campaign_spend)) +
  geom_histogram(bins = 30, fill = "steelblue", alpha = 0.7) +
  facet_wrap(~campaign_variant, ncol = 1) +
  labs(
    title = "Campaign Spend Distribution by Variant (Faceted)",
    x = "Campaign Spend ($)",
    y = "Count"
  ) +
  theme_minimal()
```

## Question 2 Model Selection

Since `campaign_spend` is a continuous positive variable (dollar amounts), we should consider:

1. **Linear Regression**: Standard approach for continuous outcomes
2. **Gamma Regression**: Better for skewed positive continuous data
3. **Log-transformed Linear Regression**: If spend is log-normally distributed
4. **ANOVA/ANCOVA**: To test differences between campaign variants while controlling for covariates

```{r q2-spend-checks}
# Check distribution of campaign spend
ggplot(data, aes(x = campaign_spend)) +
  geom_histogram(bins = 50, fill = "steelblue", alpha = 0.7) +
  labs(title = "Campaign Spend Distribution", x = "Campaign Spend ($)", y = "Count") +
  theme_minimal()

# Check log-transformed spend
ggplot(data, aes(x = log(campaign_spend))) +
  geom_histogram(bins = 50, fill = "darkgreen", alpha = 0.7) +
  labs(title = "Log Campaign Spend Distribution", x = "Log(Campaign Spend)", y = "Count") +
  theme_minimal()

# Q-Q plot
qqnorm(data$campaign_spend)
qqline(data$campaign_spend, col = "red")
```

## Question 2 Models

### Model 1: Linear Regression with Campaign Variant Only

```{r q2-model-lm-simple}
# Simple linear model with campaign variant
model_q2_lm_simple <- lm(campaign_spend ~ campaign_variant, data = data)

# Summary
summary(model_q2_lm_simple)

# Tidy output
tidy(model_q2_lm_simple, conf.int = TRUE) %>%
  kable(digits = 3, caption = "Linear Model: Campaign Variant Only")

# ANOVA
anova(model_q2_lm_simple) %>%
  kable(digits = 3, caption = "ANOVA: Campaign Variant Effect")
```

### Model 2: Linear Regression with Covariates (ANCOVA)

```{r q2-model-lm-full}
# Full linear model with covariates
model_q2_lm_full <- lm(
  campaign_spend ~ campaign_variant + age + gender + past_purchases + email_signup + ad_source,
  data = data
)

# Summary
summary(model_q2_lm_full)

# Tidy output
tidy(model_q2_lm_full, conf.int = TRUE) %>%
  kable(digits = 3, caption = "Linear Model: Full Model with Covariates")

# Type III ANOVA (for unbalanced designs)
Anova(model_q2_lm_full, type = "III") %>%
  kable(digits = 3, caption = "Type III ANOVA: Testing Each Predictor")
```

### Model 3: Gamma Regression (GLM)

```{r q2-model-gamma}
# Gamma regression (better for skewed positive continuous data)
model_q2_gamma <- glm(
  campaign_spend ~ campaign_variant + age + gender + past_purchases + email_signup + ad_source,
  family = Gamma(link = "log"),
  data = data
)

# Summary
summary(model_q2_gamma)

# Tidy output
tidy(model_q2_gamma, conf.int = TRUE) %>%
  kable(digits = 3, caption = "Gamma Regression: Full Model")
```

### Model 4: Linear Regression with Interactions

```{r q2-model-interactions}
# Model with interaction between campaign variant and key predictors
model_q2_interaction <- lm(
  campaign_spend ~ campaign_variant * (age + past_purchases + email_signup),
  data = data
)

# Summary
summary(model_q2_interaction)

# ANOVA to test interactions
anova(model_q2_lm_full, model_q2_interaction) %>%
  kable(digits = 3, caption = "Model Comparison: Testing Interactions")
```

## Question 2 Model Diagnostics

```{r q2-diagnostics}
# Residual plots for full linear model
par(mfrow = c(2, 2))
plot(model_q2_lm_full)
par(mfrow = c(1, 1))

# Check model assumptions
check_model(model_q2_lm_full)
```

```{r q2-predictions}
# Predicted values
data_q2_pred <- data %>%
  mutate(
    predicted_lm = predict(model_q2_lm_full),
    predicted_gamma = predict(model_q2_gamma, type = "response")
  )

# Plot predictions
ggplot(data_q2_pred, aes(x = predicted_lm, y = campaign_spend)) +
  geom_point(alpha = 0.3, color = "steelblue") +
  geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") +
  labs(
    title = "Predicted vs Actual Campaign Spend (Linear Model)",
    x = "Predicted Spend ($)",
    y = "Actual Spend ($)"
  ) +
  theme_minimal()
```

## Question 2 Pairwise Comparisons

```{r q2-pairwise}
# Post-hoc pairwise comparisons using Tukey's HSD
model_q2_aov <- aov(campaign_spend ~ campaign_variant + age + gender + past_purchases + email_signup + ad_source, data = data)

# Tukey HSD for campaign variant
tukey_results <- TukeyHSD(model_q2_aov, "campaign_variant")
tukey_results

# Visualize pairwise comparisons
plot(tukey_results, las = 1)

# Create tidy version
tukey_df <- as.data.frame(tukey_results$campaign_variant)
tukey_df$comparison <- rownames(tukey_df)
tukey_df %>%
  select(comparison, diff, lwr, upr, `p adj`) %>%
  kable(digits = 3, caption = "Tukey HSD: Pairwise Comparisons of Campaign Variants")
```

## Question 2 Effect Size Analysis

```{r q2-effect-size}
# Calculate effect sizes (Cohen's d) for each pairwise comparison
library(effectsize)

# Effect size for campaign variants
cohens_d(campaign_spend ~ campaign_variant, data = data) %>%
  kable(digits = 3, caption = "Cohen's d: Effect Sizes for Campaign Variants")

# Calculate mean differences and confidence intervals
emmeans_results <- emmeans::emmeans(model_q2_lm_full, ~ campaign_variant)
emmeans_contrasts <- emmeans::contrast(emmeans_results, method = "pairwise")

# Display results
summary(emmeans_results) %>%
  kable(digits = 2, caption = "Estimated Marginal Means by Campaign Variant")

summary(emmeans_contrasts) %>%
  kable(digits = 2, caption = "Pairwise Contrasts of Campaign Variants")
```

## Question 2 Visualize Campaign Performance

```{r q2-visualize-performance}
# Predicted means with confidence intervals
emmeans_df <- as.data.frame(summary(emmeans_results))

ggplot(emmeans_df, aes(x = campaign_variant, y = emmean)) +
  geom_point(size = 4, color = "steelblue") +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.2, linewidth = 1) +
  labs(
    title = "Estimated Campaign Spend by Variant (Adjusted for Covariates)",
    x = "Campaign Variant",
    y = "Estimated Mean Spend ($)"
  ) +
  theme_minimal()
```

## Question 2 Subgroup Analysis

```{r q2-subgroups}
# Analyze campaign performance by key subgroups

# By email signup status
data %>%
  group_by(campaign_variant, email_signup) %>%
  summarise(
    mean_spend = mean(campaign_spend),
    se_spend = sd(campaign_spend) / sqrt(n()),
    n = n()
  ) %>%
  ggplot(aes(x = campaign_variant, y = mean_spend, fill = email_signup)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
  geom_errorbar(aes(ymin = mean_spend - 1.96 * se_spend, ymax = mean_spend + 1.96 * se_spend),
    position = position_dodge(0.9), width = 0.2
  ) +
  labs(
    title = "Campaign Spend by Variant and Email Signup",
    x = "Campaign Variant",
    y = "Mean Spend ($)",
    fill = "Email Signup"
  ) +
  theme_minimal()

# By age group
data %>%
  mutate(age_group = cut(age, breaks = c(0, 30, 45, 60, 100), labels = c("18-30", "31-45", "46-60", "60+"))) %>%
  group_by(campaign_variant, age_group) %>%
  summarise(
    mean_spend = mean(campaign_spend),
    se_spend = sd(campaign_spend) / sqrt(n()),
    n = n()
  ) %>%
  ggplot(aes(x = campaign_variant, y = mean_spend, fill = age_group)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
  geom_errorbar(aes(ymin = mean_spend - 1.96 * se_spend, ymax = mean_spend + 1.96 * se_spend),
    position = position_dodge(0.9), width = 0.2
  ) +
  labs(
    title = "Campaign Spend by Variant and Age Group",
    x = "Campaign Variant",
    y = "Mean Spend ($)",
    fill = "Age Group"
  ) +
  theme_minimal()
```

## Question 2 Key Findings Summary

```{r q2-summary-table}
# Create comprehensive summary by campaign variant
data %>%
  group_by(campaign_variant) %>%
  summarise(
    n = n(),
    mean_spend = mean(campaign_spend),
    median_spend = median(campaign_spend),
    sd_spend = sd(campaign_spend),
    total_revenue = sum(campaign_spend),
    pct_above_100 = mean(campaign_spend > 100) * 100,
    pct_above_200 = mean(campaign_spend > 200) * 100
  ) %>%
  kable(digits = 2, caption = "Comprehensive Campaign Performance Summary")
```

---

# Model Comparison and Selection

```{r model-comparison}
# Compare all models using AIC
model_comparison <- data.frame(
  Model = c("Q1: NB Full", "Q1: NB Simple", "Q1: Poisson", "Q1: GAM",
            "Q2: LM Simple", "Q2: LM Full", "Q2: Gamma", "Q2: LM Interaction"),
  AIC = c(
    AIC(model_q1_nb),
    AIC(model_q1_nb_simple),
    AIC(model_q1_poisson),
    AIC(model_q1_gam),
    AIC(model_q2_lm_simple),
    AIC(model_q2_lm_full),
    AIC(model_q2_gamma),
    AIC(model_q2_interaction)
  ),
  BIC = c(
    BIC(model_q1_nb),
    BIC(model_q1_nb_simple),
    BIC(model_q1_poisson),
    BIC(model_q1_gam),
    BIC(model_q2_lm_simple),
    BIC(model_q2_lm_full),
    BIC(model_q2_gamma),
    BIC(model_q2_interaction)
  )
)

model_comparison %>%
  kable(digits = 2, caption = "Model Comparison: AIC and BIC")
```

# Final Summary

## Question 1: Characteristics of High Purchasers

Based on the Negative Binomial regression analysis:

- **Best Model**: `r ifelse(AIC(model_q1_nb) < AIC(model_q1_nb_simple), "Full Negative Binomial", "Simplified Negative Binomial")`
- **Key Predictors**: Age, email signup status, and campaign spend are most important
- **Model Performance**: Explains variation in past purchases while accounting for overdispersion

## Question 2: Optimal Campaign Variant

Based on the ANCOVA and pairwise comparison analysis:

- **Best Model**: Linear regression with covariates (ANCOVA)
- **Recommended Variant**: Based on adjusted means and statistical significance
- **Key Considerations**: Effect sizes, subgroup differences, and business impact

```{r final-recommendations}
# Extract key numbers for final recommendation
variant_means <- data %>%
  group_by(campaign_variant) %>%
  summarise(
    mean_spend = mean(campaign_spend),
    n = n(),
    total_revenue = sum(campaign_spend)
  ) %>%
  arrange(desc(mean_spend))

cat("\nCampaign Variant Rankings by Average Spend:\n")
print(variant_means)

# Calculate revenue difference
max_revenue_variant <- variant_means$campaign_variant[1]
revenue_diff <- variant_means$mean_spend[1] - variant_means$mean_spend[3]
pct_improvement <- (revenue_diff / variant_means$mean_spend[3]) * 100

cat("\nBest Performing Variant:", as.character(max_revenue_variant), "\n")
cat("Revenue improvement vs worst variant: $", round(revenue_diff, 2),
    " (", round(pct_improvement, 1), "%)\n", sep = "")
```

---

# Session Information

```{r session-info}
sessionInfo()
```
